\myTitle

### 2024-01-10 tex/body-text-of-paper.tex
Added some edits to SNPtype conversion
Added Yoshiyama historical paper citation
quick edit

For the candidate markers found by the above process, we designed amplification primers using 
Primer3 \citep{koressaar2007enhancements,untergasser2012primer3} and tested amplification in a 
subset of Chinook salmon 
samples. The primer pairs that amplified sequence that reliably mapped back to the association- 
peak region were then typed
in a separate collection of 1,638 Sacramento River Chinook salmon sampled from the fish trap below Keswick Dam, including 1,169 winter run, 281 spring 
run, and 188 fall/late-fall run. We divided the fish identified as fall/late-fall via the 125-locus genetic 
stock identification data set into fall run and late fall run according to their sampling date at Keswick: 
99 fish arriving before Dec 26 were classified as fall run and 89 fish arriving after Dec 26 were 
classified as late-fall run.   The allele frequencies of the target SNPs at the remaining amplicons 
were 
estimated for each of these four groups: winter, spring, fall, and late-fall, and we retained
amplicons showing large allele frequency  differences between late-fall fish and all other runs.

>>>>

For the candidate markers found by the above process, we designed amplification primers using 
Primer3 \citep{koressaar2007enhancements,untergasser2012primer3} and tested amplification in a 
subset of Chinook salmon 
samples. The primer pairs that amplified sequence that reliably mapped back to the association-peak region were then typed
in a separate collection of 1,638 Sacramento River Chinook salmon sampled from the fish trap below Keswick Dam, including 1,169 winter run, 281 spring 
run, and 188 fall/late-fall run. We divided the fish identified as fall/late-fall via the 125-locus genetic 
stock identification data set into fall run and late fall run according to their sampling date at Keswick: 
99 fish arriving before Dec 26 were classified as fall run and 89 fish arriving after Dec 26 were 
classified as late-fall run.   The allele frequencies of the target SNPs at the remaining amplicons 
were 
estimated for each of these four groups: winter, spring, fall, and late-fall, and we retained
amplicons showing large allele frequency  differences between late-fall fish and all other runs.
